---
title: "Air Pollution Survey Analysis"
format: pdf
editor: visual
execute:
  echo: false
  message: false
  warning: false
---

Notes from meeting: standardize perceived risk scores to perceived risk proportion: add perceived risk for pm2.5 (call it perceived threat pm2.5) and 03 (perceived threat 03) rows, and grand total Change knowledge scores

Notes from March 27: add in ranked scatterplots of IO level and difference

Meeting Notes: table and graph constructs in the same order,

images should be jpegs (9pt arial font for figure labels)

## Methods:

The analysis focuses on differences in pre and post intervention survey responses related to pollutant risk perception. We first found that among the 15 subjects who completed both surveys, 2 surveys had a small number (6) of non-responses. We impute these responses using KNN imputation from the VIM package in R. Next, we conducted a confirmatory factor analysis in SAS on questionnaire responses with perceived susceptibility and perceived sustainability as latent factors. Results didn't produce a good enough fit to confirm these as underlying factors related to the answering of the survey questions. Next, we perform two-sided t-tests on overall risk score differences and risk score differences broken down by risk perception constructs (as defined by survey designers). Due to differing maximum risk scores for each construct, we standardize risk scores by dividing by the total possible risk score for each construct. We also perform two-sided t-tests on overall pollutant knowledge score differences. Finally, we explore the relationship between the actual pollutant level in an individual's home and their perceived risk. We do this by fitting linear models with perceived risk score difference as the response and pollutant level as the covariate. We also perform ranked spearman correlation tests on these same variables to explore ranked correlation.

## Data

House 6 Pre-Intervention has NAs for Q12 and Q13. House 33 Pre-Intervention has an NA for Q11. We used KNN imputation to impute these missing values for the analysis.

```{r}

library(tidyverse)
library(ggsignif)
# set theming

theme_set(
  theme_minimal(base_family = "Arial", base_size = 9)
)

## read in updated survey_aq_data from survey_behavior.r to have the updates to the behavior questions
df_raw <- read_csv("./Processed Data/survey_aq_updated.csv")

# create dataframe used for factor analysis
fa_df <- df_raw %>%
  select(HouseID, Survey, QuestionID, Score_mod) %>%
  filter(QuestionID %in% paste0("Q", sprintf("%02d", 9:22))) %>%
  pivot_wider(id_cols = c(HouseID, Survey), names_from = QuestionID, values_from = Score_mod) %>%
  filter(HouseID != "H29") # H29 survey is all NAs
  #select(-c(1,2)) %>%

# impute NA values
library(VIM)

dim(fa_df) #(30,16)


fa_df_imputed <- kNN(fa_df %>% dplyr::select(-c(HouseID, Survey))) %>%
  select(1:(ncol(fa_df)-2)) %>%
  mutate(HouseID = fa_df$HouseID,
         Survey = fa_df$Survey)

write_csv(fa_df_imputed, "factor_analysis_df.csv")

```

```{r}

## relationship with behavior change, threat and knowledge




# create dataframe used for factor analysis
fa_df_29 <- df_raw %>%
  select(HouseID, Survey, QuestionID, Score_mod) %>%
  filter(QuestionID %in% paste0("Q", sprintf("%02d", 9:22))) %>%
  pivot_wider(id_cols = c(HouseID, Survey), names_from = QuestionID, values_from = Score_mod) |> 
  filter(HouseID == "H29")

## let's use House ID 29, even though we didn't use it in the factor analysis. 

fa_df_imputed_29 <- fa_df_imputed |> 
  bind_rows(fa_df_29)

model_df_long <- fa_df_imputed_29 %>% 
  mutate(total_score =  rowSums(across(Q09:Q22))) %>%
  select(HouseID, Survey, total_score) 

```

```{r}

## merge some of the questions back into the main dataset to have the updated behavior questions in the main dataset for analysis

## read in data from survey_behavior.r

survey_aq_updated <- read_csv("./Processed Data/survey_aq_updated.csv")

names(survey_aq_updated)

behavior_df <- survey_aq_updated %>%
  filter(QuestionID %in% c("Q25", "Q29")) %>%
  select(HouseID, Survey, ac.type, QuestionID, Response,mean_IO_PM_Summer,mean_IO_O3_Summer)

## get metadata 

metadata <- behavior_df %>%
  filter(QuestionID %in% c("Q25")) %>%
  filter(Survey == "Pre_Intervention") %>%
  select(HouseID, ac.type)

```


Look at change in knowledge vs. change in threats, create a dataframe that has the imputed risk responses and the knowledge scores.

```{r}
## combine fa_df_imputed with the knowledge scores 

names(fa_df_imputed)
names(knowledge_df)
names(knowledge03_df)

Create risk scores from fa_df_imputed by the different categories and PM levels. 

Then merge that to the knowledge scores. 

fa_df_imputed_scores <- fa_df_imputed %>%  
  mutate(PM2.5_susceptibility_score = rowSums(across(c(Q09,Q10,Q11,Q13)))/(5*4), # divide by total possible score for these questions to get a proportion
         O3_susceptibility_score = rowSums(across(c(Q17,Q18,Q19,Q21)))/(5*4),
         PM2.5_severity_score = rowSums(across(c(Q12,Q14)))/(5*2),
         O3_severity_score = rowSums(across(c(Q15,Q16,Q20,Q22)))/(5*4),
         threat_score = (PM2.5_susceptibility_score + O3_susceptibility_score + PM2.5_severity_score + O3_severity_score)/4) # average of the 4 scores to get an overall threat score

risk_diff <- fa_df_imputed_scores |> 
  select(HouseID, Survey, O3_susceptibility_score, O3_severity_score, PM2.5_susceptibility_score, PM2.5_severity_score, threat_score) |>
  pivot_longer(cols = c(O3_susceptibility_score, O3_severity_score, PM2.5_susceptibility_score, PM2.5_severity_score, threat_score), names_to = 'type', values_to = 'score') |> 
  pivot_wider(id_cols = c(HouseID,type), names_from = Survey, values_from = score) |>
  mutate(risk_diff = `Post_Intervention` - `Pre_Intervention`) |>
  select(HouseID, type, risk_diff) |> 
  pivot_wider(id_cols = HouseID, names_from = type, values_from = risk_diff) 

threat_knowledge_df <- risk_diff %>%
  left_join(knowledge_df |> select(HouseID, difference) |> rename(knowledge_total_diff = difference), by = c("HouseID")) |> 
  left_join(knowledge03_df |> select(HouseID, difference) |> rename(knowledge_O3_diff = difference), by = c("HouseID")) |> 
  left_join(knowledgepm_df |> select(HouseID, difference) |> rename(knowledge_PM_diff = difference), by = c("HouseID")) |> 
  left_join(metadata, by = "HouseID") |> 
  rename(Total_threat_score = threat_score) 

```


Make graphs between difference in knowledge and threat scores

Total knowledge and total threat

```{r}
library(ggplot2)
library(patchwork)

# --- Function ---
plot_knowledge_threat <- function(df, x_var, y_var, x_label, y_label) {
  
  lm_fit     <- lm(reformulate(x_var, y_var), data = df)
  lm_summary <- summary(lm_fit)
  p_val      <- lm_summary$coefficients[2, 4]
  r_sq       <- lm_summary$r.squared
  
  p_label <- if (p_val < 0.001) {
    sprintf("R² = %.3f, p < 0.001", r_sq)
  } else {
    sprintf("R² = %.3f, p = %.3f", r_sq, p_val)
  }
  
  ggplot(df, aes(x = .data[[x_var]], y = .data[[y_var]])) +
    geom_point(aes(shape = ac.type, color = ac.type)) +
    geom_smooth(method = "lm", se = TRUE, color = "black") +
    annotate(
      "text",
      x = Inf, y = Inf,
      label = p_label,
      hjust = 1.05, vjust = 1.5,
      size = 3, fontface = "italic"
    ) +
    labs(x = x_label, y = y_label, color = "House Type", shape = "House Type") +
    scale_color_manual(values = okabe_ito, name = "House Type") +
    scale_shape_manual(values = c(16, 17), name = "House Type") +
    theme_bw() +
    theme(legend.position = "none")  # suppress per-panel legends; add combined below
}

# --- Define variable pairs & axis labels ---
plot_specs <- list(
  list(x = "knowledge_total_diff", y = "Total_threat_score",
       xl = "Total Knowledge Score",       yl = "Total Threat Score"),
  list(x = "knowledge_O3_diff",    y = "O3_susceptibility_score",
       xl = "O3 Knowledge Score",          yl = "O3 Susceptibility Score"),
  list(x = "knowledge_O3_diff",    y = "O3_severity_score",
       xl = "O3 Knowledge Score",          yl = "O3 Severity Score"),
  list(x = "knowledge_PM_diff",    y = "PM2.5_susceptibility_score",
       xl = "PM2.5 Knowledge Score",       yl = "PM2.5 Susceptibility Score"),
  list(x = "knowledge_PM_diff",    y = "PM2.5_severity_score",
       xl = "PM2.5 Knowledge Score",       yl = "PM2.5 Severity Score")
)

# --- Build plots ---
plots <- lapply(plot_specs, function(s) {
  plot_knowledge_threat(threat_knowledge_df, s$x, s$y, s$xl, s$yl)
})

# --- Extract shared legend from one plot (re-enable legend temporarily) ---
legend_plot <- plots[[1]] + theme(legend.position = "bottom")
shared_legend <- cowplot::get_legend(legend_plot)

# --- Combine with patchwork + shared legend ---
combined <- (plots[[1]] | plot_spacer()) / (plots[[2]] | plots[[3]]) /
            (plots[[4]] | plots[[5]] ) 


final_plot <- combined + 
  plot_layout(guides = "collect") &   
  theme(legend.position = "right")

final_plot

ggsave(
  plot = final_plot,
  filename = "./Graphics/knowledge_threat_combined.jpeg",
  width = 7, height = 10, dpi = 300, units = "in", bg = "white"
)
```


```{r}

# Fit the model to extract p-value
lm_fit <- lm(threat_score ~ threat_score, data = threat_knowledge_df)
lm_summary <- summary(lm_fit)

# Extract p-value for the slope
p_val <- lm_summary$coefficients[2, 4]
r_sq   <- lm_summary$r.squared

# Format label
p_label <- if (p_val < 0.001) {
  sprintf("R² = %.3f, p < 0.001", r_sq)
} else {
  sprintf("R² = %.3f, p = %.3f", r_sq, p_val)
}

ggplot(threat_knowledge_df, aes(x = threat_score, y = PM2.5_susceptibility_score)) +
  geom_point(aes(shape = ac.type, color = ac.type)) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate(
    "text",
    x = Inf, y = Inf,
    label = p_label,
    hjust = 1.05, vjust = 1.5,
    size = 3.5,
    fontface = "italic"
  ) +
  labs(
    x = "PM2.5 Knowledge Score",
    y = "PM2.5 Susceptibility Score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  scale_color_manual(values = okabe_ito, name = "House Type") +
  scale_shape_manual(values = c(16, 17), name = "House Type") +
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white",
       filename = "./Graphics/PM_knowledge_susceptibility_diff_plot.jpeg")


names(threat_knowledge_df)

## Compare linear model between knowledge scores and threat scores.

ggplot(threat_knowledge_df, aes(x = knowledge_total_diff, y = threat_score)) +
   geom_point(aes(shape = ac.type, color = ac.type))+
   geom_smooth(method = "lm", se = TRUE, color = "black") +
  labs(
    x = "Knowledge Score",
    y = "Threat Score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  #scale_color_grey()+
 scale_color_manual(values = okabe_ito, name = "House Type") +
 scale_shape_manual(values = c(16,17), name = "House Type") +
   #guides(shape = "none") + 
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/knowledge_threat_diff_plot.jpeg")

```

PM knowledge and PM threat

```{r}

# Fit the model to extract p-value
lm_fit <- lm(PM2.5_susceptibility_score ~ knowledge_PM_diff, data = threat_knowledge_df)
lm_summary <- summary(lm_fit)

# Extract p-value for the slope
p_val <- lm_summary$coefficients[2, 4]
r_sq   <- lm_summary$r.squared

# Format label
p_label <- if (p_val < 0.001) {
  sprintf("R² = %.3f, p < 0.001", r_sq)
} else {
  sprintf("R² = %.3f, p = %.3f", r_sq, p_val)
}

ggplot(threat_knowledge_df, aes(x = knowledge_PM_diff, y = PM2.5_susceptibility_score)) +
  geom_point(aes(shape = ac.type, color = ac.type)) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate(
    "text",
    x = Inf, y = Inf,
    label = p_label,
    hjust = 1.05, vjust = 1.5,
    size = 3.5,
    fontface = "italic"
  ) +
  labs(
    x = "PM2.5 Knowledge Score",
    y = "PM2.5 Susceptibility Score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  scale_color_manual(values = okabe_ito, name = "House Type") +
  scale_shape_manual(values = c(16, 17), name = "House Type") +
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white",
       filename = "./Graphics/PM_knowledge_susceptibility_diff_plot.jpeg")
```







```{r}


threat_behavior_score_Q25 <- model_df_long %>%
  left_join(behavior_df, by = c("HouseID", "Survey")) |> 
  mutate(Survey = factor(Survey, levels = c("Pre_Intervention", "Post_Intervention"), ordered = TRUE)) |>
  filter(QuestionID == "Q25") |> 
  mutate(Response = case_when(
      Response == 1 ~ "Change",
      Response == 2 ~ "No Change"
    )) |> 
  mutate(sample = case_when(
    HouseID == "H05" ~ "Post-Intervention only",
    HouseID ==  "H19" ~ "Post-Intervention only",
    HouseID == 'H29' ~ "Pre-Intervention only",
   TRUE ~ "Both" ))   |> 
  filter(!is.na(Response)) 

  
behavior_Q25_post <- threat_behavior_score_Q25 |>
  filter(Survey == "Post_Intervention") |>
  select(HouseID, Response) |> 
  mutate(Post_response = Response ) |>
  add_row(HouseID = "H29", Post_response = "No Change") |> 
  select(-Response)

threat_behavior_score_Q25_2 <- threat_behavior_score_Q25 |> 
  left_join(behavior_Q25_post, by = "HouseID") 

names(threat_behavior_score_Q25)

names(threat_behavior_score_Q25_2)

threat_behavior_score_Q25_diff <- threat_behavior_score_Q25_2 |> 
  pivot_wider(id_cols = c(HouseID, ac.type, Post_response), names_from = Survey, values_from = total_score) |> 
  mutate(score_diff = Post_Intervention - Pre_Intervention) |> 
 filter(!is.na(score_diff))



okabe_ito <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
               "#0072B2", "#D55E00", "#CC79A7", "#000000",
               "#332288", "#117733", "#44AA99", "#88CCEE",
               "#DDCC77", "#882255")

set.seed(123) # for reproducibility of jitter
ggplot(threat_behavior_score_Q25, aes(x = Response, y = total_score,color=Response)) +
  geom_boxplot(outlier.shape = NA)+
   geom_jitter(width=0.3,height=0, aes(shape = ac.type))+
  facet_wrap(~Survey, labeller = labeller(Survey = c("Pre_Intervention"= "Pre-Intervention (n=14)", "Post_Intervention" = "Post-Intervention (n=15)"))) +
    geom_signif(
    comparisons = list(c('Change', 'No Change')),
    map_signif_level = FALSE,
    test = 't.test',
    color = 'black',
    vjust = 0,
    margin_top = 0.1
  ) +
  labs(
    x = "Change in Behavior due to Outdoor Air Quality",
    y = "Threat score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  #scale_color_grey()+
 scale_color_manual(values = okabe_ito, name = "House Type") +
    guides(color = "none") + 
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/threat_behavior_plot.jpeg")

```

Figure 1 for Q29

```{r}

threat_behavior_score_Q29 <- model_df_long %>%
  left_join(behavior_df, by = c("HouseID", "Survey")) |>
  mutate(Survey = factor(Survey, levels = c("Pre_Intervention", "Post_Intervention"), ordered = TRUE)) |>
  filter(QuestionID == "Q29") |>
  mutate(Response = case_when(
      Response == 1 ~ "Change",
      Response == 2 ~ "No Change"
    )) |>
  filter(!is.na(Response))

set.seed(123)
ggplot(threat_behavior_score_Q29, aes(x = Response, y = total_score, color = Response)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.3, height = 0, aes(shape = ac.type)) +
    geom_signif(
    comparisons = list(c('Change', 'No Change')),
    map_signif_level = FALSE,
    test = 't.test',
    color = 'black',
    vjust = 0,
    margin_top = 0.1
  ) +
  facet_wrap(~Survey, labeller = labeller(Survey = c("Pre_Intervention" = "Pre-Intervention", "Post_Intervention" = "Post-Intervention"))) +
  labs(
    x = "Made changes to home to improve air quality (Q29)",
    y = "Threat score",
    color = "House Type",
    shape = "AC Type"
  ) +
  scale_color_manual(values = okabe_ito, name = "House Type") +
    guides(color = "none") + 
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/threat_behavior_plot_Q29.jpeg")

```

Make a plot showing the difference in Threat score by behavior change group, with lines connecting the same HouseID across surveys. (Figure 2 for Q25)

```{r}

## geom_point and geom_line
ggplot(threat_behavior_score_Q25_2, aes(x = Survey, y = total_score)) +
    geom_point(width=0.3,height=0, aes(shape = ac.type, color = Post_response))+
   geom_line(aes(group = HouseID), color = "grey80", alpha = 0.5) +  # add lines connecting points for the same HouseID
  facet_wrap(~Post_response) +
  labs(
    x = "Survey",
    y = "Threat score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  #scale_color_grey()+
 scale_color_manual(values = okabe_ito, name = "Behavior") +
  theme_bw()

  ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/threat_behavior_plot.jpeg")


```

Figure 3 for Question 25

```{r}
library(ggrepel)

jitter_pos <- position_jitter(width = 0.3, height = 0, seed = 42)

ggplot(threat_behavior_score_Q25_diff, aes(x = Post_response, y = score_diff, color = Post_response)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(position = jitter_pos, aes(shape = ac.type)) +
  geom_label_repel(
    aes(label = HouseID),
    position = jitter_pos,
    size = 3,
    min.segment.length = .6,  
    segment.color = "grey70", 
    color = 'grey70',
    box.padding = 0.4,
    show.legend = FALSE,
    alpha=0.7
  ) +
  labs(
    x = "Change in behavior in post-intervention survey due to Outdoor air quality",
    y = "Change in threat score",
    color = "Home ID",
    shape = "AC Type"
  ) +
  geom_signif(
    comparisons = list(c('Change', 'No Change')),
    map_signif_level = FALSE,
    test = 'wilcox.test',
    color = 'black',
    vjust = 0,
    margin_top = 0.1
  ) +
  scale_color_manual(values = okabe_ito, name = "Behavior") +
  guides(color = "none") +    
  theme_bw()


ggsave("./Graphics/diff_threat_by_behavior.tiff",
       width = 170, height = 120,
       units = "mm",
       dpi = 300,
       compression = "lzw")
```

```{r}
# overall knowledge

qs_not_to_change <- c("Q04", "Q08")

knowledge_df_wide <- df_raw %>%
  filter(Construct_general == "Knowledge") %>%
  select(HouseID, Survey, QuestionID, Score_mod) %>%
  mutate(Score_mod = case_when(!QuestionID %in% qs_not_to_change & Score_mod == -1 ~ 0,
                               TRUE ~ Score_mod)) %>%
  group_by(HouseID, Survey) %>%
  summarize(know_score = sum(Score_mod))

threat_behavior_knowledge_Q25 <- threat_behavior_score_Q25 |> 
  left_join(knowledge_df_wide, by = c("HouseID", "Survey")) |> 
  mutate(Survey = factor(Survey, levels = c("Pre_Intervention", "Post_Intervention"), ordered = TRUE)) 

ggplot(threat_behavior_knowledge_Q25, aes(x = Response, y = know_score, color = Response)) +
  geom_boxplot(outlier.shape = NA)+
   geom_jitter(width=0.3,height=0, aes(shape = ac.type))+
  #geom_signif(comparisons=list(c('Change','No Change')),
   #                            map_signif_level=FALSE,test='t.test',
   #                            color='black',vjust=0,margin_top=0.1)+
  facet_wrap(~Survey) +
  labs(
    x = "Change in Behavior due to Outdoor Air Quality",
    y = "Knowledge Score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  #scale_color_grey()+
 scale_color_manual(values = okabe_ito, name = "House Type") +
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/knowledge_behavior_plot.jpeg")

```

Figure 4 for Q29

```{r}

## Add t-tests

threat_behavior_knowledge_Q29 <- threat_behavior_score_Q29 |>
  left_join(knowledge_df_wide, by = c("HouseID", "Survey")) |>
  mutate(Survey = factor(Survey, levels = c("Pre_Intervention", "Post_Intervention"), ordered = TRUE))

ggplot(threat_behavior_knowledge_Q29, aes(x = Response, y = know_score, color = Response)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.3, height = 0, aes(shape = ac.type)) +
  facet_wrap(~Survey) +
  labs(
    x = "Change in Behavior due to Outdoor Air Quality (Q29)",
    y = "Knowledge Score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  scale_color_manual(values = okabe_ito, name = "House Type") +
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/knowledge_behavior_plot_Q29.jpeg")

```

```{r}
library(broom)

# ── T-test summaries matching the geom_signif comparisons above ──────────────

run_ttest_summary <- function(df, score_var, score_label) {
  df |>
    group_by(Survey) |>
    group_modify(~ {
      test <- t.test(as.formula(paste(score_var, "~ Response")), data = .x)
      tibble(
        `Mean (Change)`    = round(unname(test$estimate)[1], 2),
        `Mean (No Change)` = round(unname(test$estimate)[2], 2),
        `T-stat`           = round(unname(test$statistic), 2),
        `df`               = round(test$parameter, 1),
        `P-value`          = round(test$p.value, 3),
        `95% CI`           = paste0("(", round(test$conf.int[1], 2), ", ",
                                        round(test$conf.int[2], 2), ")")
      )
    }) |>
    ungroup() |>
    mutate(Outcome = score_label,
           Survey  = str_replace_all(as.character(Survey), "_", " ")) |>
    relocate(Outcome, Survey)
}

bind_rows(
  run_ttest_summary(threat_behavior_knowledge_Q25, "total_score", "Threat Score"),
  run_ttest_summary(threat_behavior_knowledge_Q25, "know_score",  "Knowledge Score")
) |>
  kable(
    booktabs = TRUE,
    caption  = "T-tests: Threat and Knowledge Scores by Behavior Change Group (Q25)"
  ) |>
  kable_styling(latex_options = "hold_position", font_size = 9, full_width = FALSE) |>
  collapse_rows(columns = 1, valign = "top")

ttest_threat_knowledge_behavior <- bind_rows(
  run_ttest_summary(threat_behavior_knowledge_Q25, "total_score", "Threat Score"),
  run_ttest_summary(threat_behavior_knowledge_Q25, "know_score",  "Knowledge Score"))

write_csv(ttest_threat_knowledge_behavior, "./Processed Data/ttest_threat_knowledge_behavior.csv")

# ── Linear models: score ~ behavior change group, by Survey ──────────────────

run_lm_by_survey <- function(df, response_var, response_label) {
  df |>
    mutate(Survey = str_replace_all(as.character(Survey), "_", " ")) |>
    group_by(Survey) |>
    group_modify(~ {
      mod <- lm(as.formula(paste(response_var, "~ Response")), data = .x)
      tidy(mod) |>
        mutate(r.squared = glance(mod)$r.squared)
    }) |>
    ungroup() |>
    mutate(
      Outcome = response_label,
      term    = str_replace(term, "ResponseNo Change", "Group: No Change"),
      term    = str_replace(term, "\\(Intercept\\)", "Intercept (Change group)")
    ) |>
    select(Outcome, Survey, term, estimate, std.error, statistic, p.value, r.squared) |>
    rename(Term = term, Estimate = estimate, `Std. Error` = std.error,
           `T-stat` = statistic, `P-value` = p.value, `R²` = r.squared) |>
    mutate(across(where(is.numeric), ~ round(., 3)))
}

bind_rows(
  run_lm_by_survey(threat_behavior_knowledge_Q25, "total_score", "Threat Score"),
  run_lm_by_survey(threat_behavior_knowledge_Q25, "know_score",  "Knowledge Score")
) |>
  kable(
    booktabs = TRUE,
    caption  = "Linear Models: Score ~ Behavior Change Group (Q25), by Survey"
  ) |>
  kable_styling(latex_options = "hold_position", font_size = 9, full_width = FALSE) |>
  collapse_rows(columns = 1:2, valign = "top")



lm_threat_knowledge_behavior <- bind_rows(
  run_lm_by_survey(threat_behavior_knowledge_Q25, "total_score", "Threat Score"),
  run_lm_by_survey(threat_behavior_knowledge_Q25, "know_score",  "Knowledge Score"))

write_csv(lm_threat_knowledge_behavior, "./Processed Data/lm_threat_knowledge_behavior.csv")

```

```{r}

## Compare linear model between knowledge scores and threat scores.

ggplot(threat_behavior_knowledge_Q25, aes(x = know_score, y = total_score)) +
   geom_point(aes(shape = ac.type, color = ac.type))+
   geom_smooth(method = "lm", se = TRUE, color = "black") +
  facet_wrap(~Survey) +
  labs(
    x = "Knowledge Score",
    y = "Threat Score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  #scale_color_grey()+
 scale_color_manual(values = okabe_ito, name = "House Type") +
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/knowledge_threat_plot.jpeg")

## What's with the two outliers?
# H28 pre-intervention knowledge is 10 times lower than the others. 
# H02 post-intervention threat score is 2 times lower than any others...
## I looked up the answers-- they aren't missing. They seem to be valid.





```

```{r}


## Compare risk perception and air quality scores, broken out by ac.type

names(threat_behavior_knowledge_Q25)



ggplot(threat_behavior_knowledge_Q25, aes(x = total_score, y = mean_IO_PM_Summer)) +
   geom_point(aes(shape = ac.type, color = ac.type))+
   geom_smooth(method = "lm", se = TRUE, color = "black") +
  facet_grid(ac.type~Survey,scales="free_y") +
  labs(
    x = "Threat Score",
    y = "PM2.5 Air Quality Score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  #scale_color_grey()+
 scale_color_manual(values = okabe_ito, name = "House Type") +
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/PM_threat.jpeg")

## combine data

ggplot(threat_behavior_knowledge_Q25, aes(x = total_score, y = mean_IO_PM_Summer)) +
   geom_point(aes(shape = ac.type, color = ac.type))+
   geom_smooth(method = "lm", se = TRUE, color = "black") +
  facet_grid(~Survey) +
  labs(
    x = "Threat Score",
    y = "PM2.5 Air Quality Score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  #scale_color_grey()+
 scale_color_manual(values = okabe_ito, name = "House Type") +
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/PM_threat_ac.jpeg")


## ozone data

ggplot(threat_behavior_knowledge_Q25, aes(x = total_score, y = mean_IO_O3_Summer)) +
   geom_point(aes(shape = ac.type, color = ac.type))+
   geom_smooth(method = "lm", se = TRUE, color = "black") +
  facet_grid(ac.type~Survey,scales="free_y") +
  labs(
    x = "Threat Score",
    y = "O3 Air Quality Score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  #scale_color_grey()+
 scale_color_manual(values = okabe_ito, name = "House Type") +
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/O3_threat_plot.jpeg")


```

```{r}
# Linear models: Air Quality ~ Threat Score
library(broom)

fit_aq_lm <- function(df, aq_var, aq_label, group_vars) {
  df |>
    mutate(Survey = str_replace_all(as.character(Survey), "_", " ")) |>
    group_by(across(all_of(group_vars))) |>
    group_modify(~ {
      mod <- lm(as.formula(paste(aq_var, "~ total_score")), data = .x)
      tidy(mod) |> mutate(r.squared = glance(mod)$r.squared)
    }) |>
    ungroup() |>
    mutate(
      Pollutant = aq_label,
      term = recode(term, "(Intercept)" = "Intercept",
                          "total_score"  = "Threat Score")
    ) |>
    select(Pollutant, all_of(group_vars), term, estimate, std.error,
           statistic, p.value, r.squared) |>
    rename(Term = term, Estimate = estimate,
           `Std. Error` = std.error, `T-stat` = statistic,
           `P-value` = p.value, `R^2` = r.squared) |>
    mutate(across(where(is.numeric), ~ round(., 3)))
}

bind_rows(
  fit_aq_lm(threat_behavior_knowledge_Q25, "mean_IO_PM_Summer", "PM2.5", "Survey"),
  fit_aq_lm(threat_behavior_knowledge_Q25, "mean_IO_O3_Summer", "O3",   "Survey")
) |>
  kable(booktabs = TRUE,
        caption = "Linear Models: Air Quality ~ Threat Score, by Survey") |>
  kable_styling(latex_options = "hold_position", font_size = 9,
                full_width = FALSE) |>
  collapse_rows(columns = 1:2, valign = "top")

bind_rows(
  fit_aq_lm(threat_behavior_knowledge_Q25, "mean_IO_PM_Summer",
            "PM2.5", c("ac.type", "Survey")),
  fit_aq_lm(threat_behavior_knowledge_Q25, "mean_IO_O3_Summer",
            "O3",   c("ac.type", "Survey"))
) |>
  kable(booktabs = TRUE,
        caption = "Linear Models: Air Quality ~ Threat Score, by AC Type and Survey") |>
  kable_styling(latex_options = "hold_position", font_size = 9,
                full_width = FALSE) |>
  collapse_rows(columns = 1:3, valign = "top")
```