---
title: "Air Pollution Survey Analysis"
format: pdf
editor: visual
execute:
  echo: false
  message: false
  warning: false
---

Notes from meeting: standardize perceived risk scores to perceived risk proportion: add perceived risk for pm2.5 (call it perceived threat pm2.5) and 03 (perceived threat 03) rows, and grand total Change knowledge scores

Notes from March 27: add in ranked scatterplots of IO level and difference

Meeting Notes: table and graph constructs in the same order,

images should be jpegs (9pt arial font for figure labels)

## Methods:

The analysis focuses on differences in pre and post intervention survey responses related to pollutant risk perception. We first found that among the 15 subjects who completed both surveys, 2 surveys had a small number (6) of non-responses. We impute these responses using KNN imputation from the VIM package in R. Next, we conducted a confirmatory factor analysis in SAS on questionnaire responses with perceived susceptibility and perceived sustainability as latent factors. Results didn't produce a good enough fit to confirm these as underlying factors related to the answering of the survey questions. Next, we perform two-sided t-tests on overall risk score differences and risk score differences broken down by risk perception constructs (as defined by survey designers). Due to differing maximum risk scores for each construct, we standardize risk scores by dividing by the total possible risk score for each construct. We also perform two-sided t-tests on overall pollutant knowledge score differences. Finally, we explore the relationship between the actual pollutant level in an individual's home and their perceived risk. We do this by fitting linear models with perceived risk score difference as the response and pollutant level as the covariate. We also perform ranked spearman correlation tests on these same variables to explore ranked correlation.

## Data

House 6 Pre-Intervention has NAs for Q12 and Q13. House 33 Pre-Intervention has an NA for Q11. We used KNN imputation to impute these missing values for the analysis.

```{r}

library(tidyverse)
library(ggsignif)
# set theming

theme_set(
  theme_minimal(base_family = "Arial", base_size = 9)
)

## read in updated survey_aq_data from survey_behavior.r to have the updates to the behavior questions
df_raw <- read_csv("./Processed Data/survey_aq_data.csv") |> 
    mutate(Score_mod = case_when(QuestionID %in% c('Q01','Q02','Q03','Q04','Q05','Q06','Q07','Q08') & HouseID == "H29"  & Survey == "Post_Intervention" ~ NA, 
                                TRUE ~ Score_mod)) ## For some reason the missing knowledge questions from H29 from the post-surveywere turned into 0, turn back to NA

# Changes single response questions from -1 to 0
# add total knowledge score test to the graphic

qs_not_to_change <- c("Q04", "Q08")



# create dataframe used for factor analysis
fa_df <- df_raw %>%
  select(HouseID, Survey, QuestionID, Score_mod) %>%
  filter(QuestionID %in% paste0("Q", sprintf("%02d", 9:22))) %>%
  pivot_wider(id_cols = c(HouseID, Survey), names_from = QuestionID, values_from = Score_mod) %>%
  filter(HouseID != "H29") # H29 survey is all NAs
  #select(-c(1,2)) %>%

# impute NA values
library(VIM)

dim(fa_df) #(30,16)


fa_df_imputed <- kNN(fa_df %>% dplyr::select(-c(HouseID, Survey))) %>%
  select(1:(ncol(fa_df)-2)) %>%
  mutate(HouseID = fa_df$HouseID,
         Survey = fa_df$Survey)

write_csv(fa_df_imputed, "factor_analysis_df.csv")

```

```{r}

## relationship with behavior change, threat and knowledge




# create dataframe used for factor analysis
fa_df_29 <- df_raw %>%
  select(HouseID, Survey, QuestionID, Score_mod) %>%
  filter(QuestionID %in% paste0("Q", sprintf("%02d", 9:22))) %>%
  pivot_wider(id_cols = c(HouseID, Survey), names_from = QuestionID, values_from = Score_mod) |> 
  filter(HouseID == "H29")

## Grab the other questions

df_non_threat_questions <- df_raw %>%
  select(HouseID, Survey, QuestionID, Score_mod) %>%
  filter(!QuestionID %in% paste0("Q", sprintf("%02d", 9:22))) %>%
  mutate(Score_mod = case_when(!QuestionID %in% qs_not_to_change & Score_mod == -1 ~ 0,
                               TRUE ~ Score_mod)) |> # # Changes single response knowledge questions from -1 to 0
  pivot_wider(id_cols = c(HouseID, Survey), names_from = QuestionID, values_from = Score_mod)  

## Bring in quesiton 29 and the other questions

fa_df_imputed_29 <- fa_df_imputed |> 
  bind_rows(fa_df_29) |>  ## add in the knowledge questions back in. 
  left_join(df_non_threat_questions, by = c("HouseID", "Survey"))  ## add in the non-threat questions back in.
  

```

```{r}

## merge some of the questions back into the main dataset to have the updated behavior questions in the main dataset for analysis

## read in data from survey_behavior.r

survey_aq_data <- read_csv("./Processed Data/survey_aq_data.csv")

## get metadata 

metadata <- survey_aq_data %>%
  filter(QuestionID %in% c("Q25")) %>%
  filter(Survey == "Pre_Intervention") %>%
  select(HouseID, ac.type, mean_IO_PM_Summer,mean_IO_O3_Summer)

```


Look at change in knowledge vs. change in threats, create a dataframe that has the imputed risk responses and the knowledge scores.

```{r}
## Calculate the scores for risk, knowledge



fa_df_imputed_scores <-  fa_df_imputed_29 %>%  
  mutate(PM2.5_susceptibility_score = rowSums(across(c(Q09,Q10,Q11,Q13)))/(5*4), # divide by total possible score for these questions to get a proportion
         O3_susceptibility_score = rowSums(across(c(Q17,Q18,Q19,Q21)))/(5*4),
         PM2.5_severity_score = rowSums(across(c(Q12,Q14)))/(5*2),
         O3_severity_score = rowSums(across(c(Q15,Q16,Q20,Q22)))/(5*4),
         PM2.5_threat_score = rowSums(across(c(Q09,Q10,Q11,Q13,Q12,Q14)))/(5*6),
         O3_threat_score = rowSums(across(c(Q17,Q18,Q19,Q21,Q15,Q16,Q20,Q22)))/(5*8),
         threat_score = rowSums(across(c(Q09:Q22)))/(5*14),
         PM2.5_knowledge_score = rowSums(across(c(Q01:Q04))), 
         O3_knowledge_score = rowSums(across(c(Q05:Q08))),
         knowledge_score = rowSums(across(c(Q01:Q08)))
         ) # 

## place into a long format
df_pre_post_scores <- fa_df_imputed_scores |> 
  select(HouseID, Survey, O3_susceptibility_score, O3_severity_score, PM2.5_susceptibility_score, PM2.5_severity_score, PM2.5_threat_score, O3_threat_score,threat_score, PM2.5_knowledge_score, O3_knowledge_score, knowledge_score) |>
  pivot_longer(cols = c(O3_susceptibility_score, O3_severity_score, PM2.5_susceptibility_score, PM2.5_severity_score, PM2.5_threat_score, O3_threat_score, threat_score, PM2.5_knowledge_score, O3_knowledge_score, knowledge_score), names_to = 'type', values_to = 'score') |> 
  left_join(metadata, by = "HouseID") |> 
  mutate(Survey = factor(Survey, levels = c("Pre_Intervention", "Post_Intervention"), labels = c("Pre-Intervention", "Post-Intervention"), ordered = TRUE)) |> 
  mutate(type = factor(type, levels = c("O3_susceptibility_score", "O3_severity_score", "O3_threat_score","PM2.5_susceptibility_score", "PM2.5_severity_score", "PM2.5_threat_score","threat_score","knowledge_score", "O3_knowledge_score", "PM2.5_knowledge_score"),
                       labels = c("O3 Susceptibility", "O3 Severity", "O3 Threat","PM2.5 Susceptibility", "PM2.5 Severity", "PM2.5 Threat","Total Threat", "Total Knowledge", "O3 Knowledge", "PM2.5 Knowledge"),
                       ordered = TRUE))


## Calculate the differences pre- and post

df_diff <- df_pre_post_scores |> 
  pivot_wider(id_cols = c(HouseID,type,ac.type,mean_IO_PM_Summer,mean_IO_O3_Summer), names_from = Survey, values_from = score) |>
  mutate(diff_score = `Post-Intervention` - `Pre-Intervention`) |>
  select(HouseID, ac.type, type, mean_IO_PM_Summer,mean_IO_O3_Summer ,diff_score) |> 
  pivot_wider(id_cols = c(HouseID,ac.type,mean_IO_PM_Summer,mean_IO_O3_Summer), names_from = type, values_from = diff_score) 


```

Make Figure S-1 (points and lines showing changes in threat before and after faceted by construct/pollutant)

```{r}

df_pre_post_threat <- df_pre_post_scores |> 
  filter(type %in% c("O3 Susceptibility", "O3 Severity", "O3 Threat","PM2.5 Susceptibility", "PM2.5 Severity", "PM2.5 Threat"))
   
   
okabe_ito <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
               "#0072B2", "#D55E00", "#CC79A7", "#000000",
               "#332288", "#117733", "#44AA99", "#88CCEE",
               "#DDCC77", "#882255")


## geom_point and geom_line
ggplot(df_pre_post_threat, aes(x = Survey, y = score)) +
    geom_point(width=0.3,height=0, aes(shape = ac.type, color = ac.type))+
   geom_line(aes(group = HouseID), color = "grey80", alpha = 0.5) +  # add lines connecting points for the same HouseID
  facet_wrap(~type) +
  labs(
    x = "Survey",
    y = "Threat score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  theme_bw() +
  theme(legend.position = "bottom") +
 scale_color_manual(values = okabe_ito, name = "House Type") +
 scale_shape_manual(values = c(16, 17), name = "House Type") 

  ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/threat_overall_change_lines.jpeg")



```


```{r}

# --- Shared Deming regression helpers ---

# Bootstrap 95% CI for mean prediction (like nlsBootPredict)
boot_ci <- function(x, y, x_grid, niter = 500) {
  set.seed(42)
  boot_mat <- replicate(niter, {
    idx <- sample(length(x), replace = TRUE)
    fit <- tryCatch(
      deming::deming(y[idx] ~ x[idx]),
      error = function(e) NULL
    )
    if (is.null(fit)) rep(NA_real_, length(x_grid))
    else fit$coefficients[1] + fit$coefficients[2] * x_grid
  })
  data.frame(
    `2.5%`  = apply(boot_mat, 1, quantile, 0.025, na.rm = TRUE),
    `97.5%` = apply(boot_mat, 1, quantile, 0.975, na.rm = TRUE),
    check.names = FALSE
  )
}

# One scatter panel from long-format df_pre_post_scores
# x_scale / y_scale: optional ggplot scale objects for axis limits/breaks
make_deming_panel <- function(df, x_type, y_type, survey_label = NULL,
                               xlim = NULL, ylim = NULL,
                               x_breaks = NULL, y_breaks = NULL,
                               niter = 500, show_ci = TRUE) {
  d <- df |> filter(type %in% c(x_type, y_type))
  if (!is.null(survey_label)) d <- d |> filter(Survey == survey_label)
  d <- d |>
    mutate(type = as.character(type)) |>
    pivot_wider(id_cols = c(HouseID, ac.type), names_from = type, values_from = score) |>
    rename(x_val = all_of(x_type), y_val = all_of(y_type))

  dem_fit   <- deming::deming(y_val ~ x_val, data = d)
  intercept <- dem_fit$coefficients[1]
  slope     <- dem_fit$coefficients[2]
  slope_se  <- dem_fit$se[2]
  t_stat    <- slope / slope_se
  p_val     <- 2 * pt(abs(t_stat), df = nrow(d) - 2, lower.tail = FALSE)
  r_sq      <- cor(d$x_val, d$y_val, use = "complete.obs")^2
  p_label   <- if (p_val < 0.001) sprintf("R² = %.3f, p < 0.001", r_sq)
               else sprintf("R² = %.3f, p = %.3f", r_sq, p_val)

  x_seq     <- seq(min(d$x_val, na.rm = TRUE), max(d$x_val, na.rm = TRUE), length.out = 50)
  ci        <- boot_ci(d$x_val, d$y_val, x_seq, niter)
  intervals <- bind_cols(data.frame(x_val = x_seq, .fitted = intercept + slope * x_seq), ci)

  p <- ggplot(d, aes(x = x_val, y = y_val)) +
    { if (show_ci) geom_ribbon(data = intervals, aes(x = x_val, ymin = `2.5%`, ymax = `97.5%`),
                inherit.aes = FALSE, alpha = 0.3, fill = "grey") } +
    geom_line(data = intervals, aes(x = x_val, y = .fitted), color = "black") +
    geom_point(aes(shape = ac.type, color = ac.type)) +
    annotate("text", x = Inf, y = Inf, label = p_label,
             hjust = 1.05, vjust = 1.5, size = 3, fontface = "italic") +
    labs(title = survey_label,
         x = if (is.null(survey_label)) paste("Difference in", x_type) else paste(x_type, "Score"),
         y = if (is.null(survey_label)) paste("Difference in", y_type) else paste(y_type, "Score"),
         color = "House Type", shape = "House Type") +
    scale_color_manual(values = okabe_ito, name = "House Type") +
    scale_shape_manual(values = c(16, 17), name = "House Type") +
    scale_x_continuous(breaks = x_breaks, labels = scales::label_number()) +
    scale_y_continuous(breaks = y_breaks, labels = scales::label_number()) +
    coord_cartesian(xlim = xlim, ylim = ylim) +
    theme_bw() +
    theme(legend.position = "none")

  p
}

# One scatter panel from wide-format df_diff with column names as x/y (difference scores)
make_deming_panel_diff <- function(df, x_var, y_var,
                                   xlim = NULL, ylim = NULL,
                                   x_breaks = NULL, y_breaks = NULL) {
  x <- df[[x_var]]
  y <- df[[y_var]]

  dem_fit   <- deming::deming(y ~ x)
  intercept <- dem_fit$coefficients[1]
  slope     <- dem_fit$coefficients[2]
  slope_se  <- dem_fit$se[2]
  t_stat    <- slope / slope_se
  p_val     <- 2 * pt(abs(t_stat), df = length(na.omit(x)) - 2, lower.tail = FALSE)
  r_sq      <- cor(x, y, use = "complete.obs")^2
  p_label   <- if (p_val < 0.001) sprintf("R² = %.3f, p < 0.001", r_sq)
               else sprintf("R² = %.3f, p = %.3f", r_sq, p_val)

  x_seq     <- seq(min(x, na.rm = TRUE), max(x, na.rm = TRUE), length.out = 50)
  ci        <- boot_ci(x, y, x_seq)
  intervals <- bind_cols(data.frame(x_val = x_seq, .fitted = intercept + slope * x_seq), ci)

  ggplot(df, aes(x = .data[[x_var]], y = .data[[y_var]])) +
    geom_ribbon(data = intervals, aes(x = x_val, ymin = `2.5%`, ymax = `97.5%`),
                inherit.aes = FALSE, alpha = 0.3, fill = "grey") +
    geom_line(data = intervals, aes(x = x_val, y = .fitted), color = "black") +
    geom_point(aes(shape = ac.type, color = ac.type)) +
    annotate("text", x = Inf, y = Inf, label = p_label,
             hjust = 1.05, vjust = 1.5, size = 3, fontface = "italic") +
    labs(x = paste("Difference in", x_var), y = paste("Difference in", y_var),
         color = "House Type", shape = "House Type") +
    scale_color_manual(values = okabe_ito, name = "House Type") +
    scale_shape_manual(values = c(16, 17), name = "House Type") +
    scale_x_continuous(breaks = x_breaks, labels = scales::label_number()) +
    scale_y_continuous(breaks = y_breaks, labels = scales::label_number()) +
    coord_cartesian(xlim = xlim, ylim = ylim) +
    theme_bw() +
    theme(legend.position = "none", axis.title = element_text(size = 9))
}

```


Compare the correlation between Severity and Susceptibility, and the correlation between Threat and Knowledge, for both O3 and PM2.5, before and after the intervention. Make scatterplots with linear regression lines and R²/p-value annotations for each of these relationships.
```{r}

xlim     <- c(0.2, 0.8)
ylim     <- c(0.3, 1.0)
x_breaks <- seq(0.2, 0.8, by = 0.2)
y_breaks <- seq(0.2, 1.0, by = 0.2)

p1 <- make_deming_panel(df_pre_post_scores, "O3 Susceptibility",   "O3 Severity",   "Pre-Intervention",  xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p2 <- make_deming_panel(df_pre_post_scores, "PM2.5 Susceptibility","PM2.5 Severity","Pre-Intervention",  xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p3 <- make_deming_panel(df_pre_post_scores, "O3 Susceptibility",   "O3 Severity",   "Post-Intervention", xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p4 <- make_deming_panel(df_pre_post_scores, "PM2.5 Susceptibility","PM2.5 Severity","Post-Intervention", xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)

final_plot <- (p1 | p2) / (p3 | p4) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
final_plot
ggsave(plot = final_plot, filename = "./Graphics/severity_susceptibility_plot.jpeg",
       width = 8, height = 8, dpi = 300, units = "in", bg = "white")

```



```{r}

df_pre_post_knowledge <- df_pre_post_scores |> 
  filter(type %in% c("Total Knowledge", "O3 Knowledge", "PM2.5 Knowledge"))

set.seed(23)   
## geom_point and geom_line
ggplot(df_pre_post_knowledge, aes(x = Survey, y = score)) +
  geom_jitter(width=0.01,height=0, aes(shape = ac.type, color = ac.type), alpha = 0.5)+
  geom_line(aes(group = HouseID), color = "grey80", alpha = 0.5) +  # add lines connecting points for the same HouseID
  facet_wrap(type~.,nrow = 1, scales = "free_y") +
  labs(
    x = "Survey",
    y = "Knowledge score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  theme_bw() +
  theme(legend.position = "bottom") +
 scale_color_manual(values = okabe_ito, name = "House Type") +
 scale_shape_manual(values = c(16, 17), name = "House Type") 

ggsave(width = 7, height = 4, dpi = 300, units = "in", bg = "white", filename = "./Graphics/knowledge_overall_change_lines.jpeg")




```





```{r}

xlim     <- c(-0.2, 4)
ylim     <- c(0.2, 0.8)
x_breaks <- seq(0, 4, by = 0.5)
y_breaks <- seq(0.2, 0.8, by = 0.2)

p1 <- make_deming_panel(df_pre_post_scores, "O3 Knowledge",    "O3 Threat",    "Pre-Intervention",  xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p2 <- make_deming_panel(df_pre_post_scores, "O3 Knowledge",    "O3 Threat",    "Post-Intervention", xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p3 <- make_deming_panel(df_pre_post_scores, "PM2.5 Knowledge", "PM2.5 Threat", "Pre-Intervention",  xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p4 <- make_deming_panel(df_pre_post_scores, "PM2.5 Knowledge", "PM2.5 Threat", "Post-Intervention", xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)

final_plot <- (p1 | p2) / (p3 | p4) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
final_plot
ggsave(plot = final_plot, filename = "./Graphics/knowledge_threat_plot.jpeg",
       width = 8, height = 8, dpi = 300, units = "in", bg = "white")

```


O3 threats vs PM2.5 Threats

```{r}

xlim     <- c(-0.2, 4)
ylim     <- c(0.2, 0.8)
x_breaks <- seq(0, 4, by = 0.5)
y_breaks <- seq(0.2, 0.8, by = 0.2)

p1 <- make_deming_panel(df_pre_post_scores, "O3 Knowledge", "O3 Susceptibility", "Pre-Intervention",  xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p2 <- make_deming_panel(df_pre_post_scores, "O3 Knowledge", "O3 Severity",       "Pre-Intervention",  xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p3 <- make_deming_panel(df_pre_post_scores, "O3 Knowledge", "O3 Threat",         "Pre-Intervention",  xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p4 <- make_deming_panel(df_pre_post_scores, "O3 Knowledge", "O3 Susceptibility", "Post-Intervention", xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p5 <- make_deming_panel(df_pre_post_scores, "O3 Knowledge", "O3 Severity",       "Post-Intervention", xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p6 <- make_deming_panel(df_pre_post_scores, "O3 Knowledge", "O3 Threat",         "Post-Intervention", xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)

final_plot <- (p1 | p2 | p3) / (p4 | p5 | p6) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
final_plot
ggsave(plot = final_plot, filename = "./Graphics/O3_knowledge_threat_plot.jpeg",
       width = 7, height = 6, dpi = 300, units = "in", bg = "white")

```

Now PM2.5

```{r}

xlim     <- c(1, 4)
ylim     <- c(0.2, 1.0)
x_breaks <- seq(1, 4, by = 0.5)
y_breaks <- seq(0.2, 1.0, by = 0.2)

p1 <- make_deming_panel(df_pre_post_scores, "PM2.5 Knowledge", "PM2.5 Susceptibility", "Pre-Intervention",  xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p2 <- make_deming_panel(df_pre_post_scores, "PM2.5 Knowledge", "PM2.5 Severity",       "Pre-Intervention",  xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p3 <- make_deming_panel(df_pre_post_scores, "PM2.5 Knowledge", "PM2.5 Threat",         "Pre-Intervention",  xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p4 <- make_deming_panel(df_pre_post_scores, "PM2.5 Knowledge", "PM2.5 Susceptibility", "Post-Intervention", xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p5 <- make_deming_panel(df_pre_post_scores, "PM2.5 Knowledge", "PM2.5 Severity",       "Post-Intervention", xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)
p6 <- make_deming_panel(df_pre_post_scores, "PM2.5 Knowledge", "PM2.5 Threat",         "Post-Intervention", xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks)

final_plot <- (p1 | p2 | p3) / (p4 | p5 | p6) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
final_plot
ggsave(plot = final_plot, filename = "./Graphics/PM2.5_knowledge_threat_plot.jpeg",
       width = 7, height = 6, dpi = 300, units = "in", bg = "white")

```



Plot O3 knowledge vs. O3 threat, and PM2.5 knowledge vs. PM2.5 threat, for pre and post intervention surveys, with linear regression lines and R²/p-value annotations.

Make graphs between difference in knowledge and threat scores

Total knowledge and total threat

```{r}
library(ggplot2)
library(patchwork)

plot_specs <- list(
  list(x = "O3 Knowledge",    y = "O3 Susceptibility"),
  list(x = "O3 Knowledge",    y = "O3 Severity"),
  list(x = "O3 Knowledge",    y = "O3 Threat"),
  list(x = "PM2.5 Knowledge", y = "PM2.5 Susceptibility"),
  list(x = "PM2.5 Knowledge", y = "PM2.5 Severity"),
  list(x = "PM2.5 Knowledge", y = "PM2.5 Threat")
)

xlim     <- c(-1, 3)
ylim     <- c(-0.6, 0.4)
x_breaks <- seq(-1, 3, by = 1)
y_breaks <- seq(-0.6, 0.4, by = 0.2)

plots <- lapply(plot_specs, function(s)
  make_deming_panel_diff(df_diff, s$x, s$y, xlim = xlim, ylim = ylim, x_breaks = x_breaks, y_breaks = y_breaks))

combined <- (plots[[1]] | plots[[2]] | plots[[3]]) /
            (plots[[4]] | plots[[5]] | plots[[6]])

final_plot <- combined +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
final_plot

ggsave(plot = final_plot, filename = "./Graphics/knowledge_threat_difference.jpeg",
       width = 7, height = 5, dpi = 300, units = "in", bg = "white")
```



Fig 1 for Q25: Threat score by behavior change group 
Create a graph showing differences in threat perception by whether they make changes to their behavior

```{r}

threat_behavior_score <- fa_df_imputed_scores%>%
  mutate(Survey = factor(Survey, levels = c("Pre_Intervention", "Post_Intervention"), labels = c("Pre-Intervention", "Post-Intervention"), ordered = TRUE)) |> 
  left_join(metadata, by = "HouseID") |> 
  mutate(Q25 = case_when(
      Q25 == 2 ~ "Change",
      Q25 == 1 ~ "No Change"
    )) |> 
  mutate(Q29 = case_when(
      Q29 == 2 ~ "Change",
      Q29 == 1 ~ "No Change" )) |>
  mutate(sample = case_when(
    HouseID == "H05" ~ "Post-Intervention only",
    HouseID ==  "H19" ~ "Post-Intervention only",
    HouseID == 'H29' ~ "Pre-Intervention only",   
   TRUE ~ "Both" ))   
  

threat_behavior_score_Q25 <- threat_behavior_score |> 
  filter(!is.na(Q25)) |> 
  select(HouseID, Survey, ac.type, Q25, sample, PM2.5_threat_score, O3_threat_score, threat_score,knowledge_score, mean_IO_PM_Summer, mean_IO_O3_Summer) 

names(threat_behavior_score)

set.seed(123) # for reproducibility of jitter
ggplot(threat_behavior_score_Q25, aes(x = Q25, y = threat_score, color=Q25)) +
  geom_boxplot(data = threat_behavior_score_Q25 |>
                 filter(!(Survey == "Pre-Intervention" & Q25 == "No Change")),
               outlier.shape = NA)+
   geom_jitter(width=0.3,height=0, aes(shape = ac.type))+
  facet_wrap(~Survey, labeller = labeller(Survey = c("Pre-Intervention"= "Pre-Intervention (n=14)", "Post-Intervention" = "Post-Intervention (n=15)"))) +
    geom_signif(
    comparisons = list(c('Change', 'No Change')),
    map_signif_level = function(p) sprintf("p = %.3f", p),
    test = 't.test',
    color = 'black',
    vjust = 0,
    margin_top = 0.1
  ) +
  labs(
    x = "Change in Behavior due to Outdoor Air Pollution(Q25)",
    y = "Threat score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  #scale_color_grey()+
 scale_color_manual(values = okabe_ito[5:6], name = "House Type") +
    guides(color = "none") + 
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/threat_behavior_plot.jpeg")

```



Figure 2 for Q25 
Threat score by behavior change group, with lines connecting the same HouseID across surveys. (Figure 2 for Q25)

```{r}

## Create a dataframe that has the post-intervention behavior responses for Q25, and merge that with the threat scores to get a dataframe that has the pre- and post- threat scores and the post-intervention responses for Q25.

behavior_Q25_post <- threat_behavior_score |>
  filter(Survey == "Post-Intervention") |>
  select(HouseID, Q25) |> 
  mutate(Post_response_Q25 = case_when(HouseID == "H29" ~ "Change", 
                  TRUE ~ Q25)) |> ## impute the response for H29 since they only have a pre-intervention survey and they said they made changes in the pre-intervention survey
  select(-Q25) |> 
  filter(!is.na(Post_response_Q25))

## join this with the threat scores, and filter to only include rows that have a post-intervention response for Q25 (i.e., remove H29 a since they only have pre-intervention surveys and we don't know their post-intervention behavior change response)

threat_behavior_score_Q25_2 <- threat_behavior_score |> 
  left_join(behavior_Q25_post, by = "HouseID") 

names(threat_behavior_score_Q25_2)

## geom_point and geom_line
ggplot(threat_behavior_score_Q25_2, aes(x = Survey, y = threat_score)) +
    geom_point(width=0.3,height=0, aes(shape = ac.type, color = Q25))+
   geom_line(aes(group = HouseID), color = "grey80", alpha = 0.5) +  # add lines connecting points for the same HouseID
  facet_wrap(~Post_response_Q25, labeller = labeller(Post_response_Q25 = c("Change" = "Change Behavior in Post-Intervention", "No Change" = "No Change in Behavior in Post-Intervention"))) +
  labs(
    x = "Survey",
    y = "Threat score",
    color = "Home Type",
    shape = "AC Type"
  ) +
    geom_label_repel(
    data = threat_behavior_score_Q25_2 |>
      filter(Post_response_Q25 == "No Change", Survey == "Post-Intervention"),
    aes(label = HouseID),
    size = 3,
    min.segment.length = .6,
    segment.color = "grey70",
    color = 'grey70',
    box.padding = 0.4,
    show.legend = FALSE,
    alpha=0.7
  ) +
  ## don't do t-test here because the groups are not independent (i.e., the same HouseIDs are in both groups since we are categorizing them based on their post-intervention response, and they have both pre- and post-intervention threat scores)
  # geom_signif(
  #   comparisons = list(c('Pre-Intervention', 'Post-Intervention')),
  #   map_signif_level = function(p) sprintf("p = %.3f", p),
  #   test = 't.test',
  #   color = 'black',
  #   vjust = 0,
  #   margin_top = 0.1
  # ) +
 scale_color_manual(values = okabe_ito[5:6], name = "Behavior") +
  theme_bw()

  ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/threat_diff_by_behavior_lines.jpeg")


```

Figure 3 for Question 25

```{r}
library(ggrepel)

threat_behavior_score_Q25_diff <- threat_behavior_score_Q25_2 |> 
  select(HouseID, ac.type, Post_response_Q25, Survey, threat_score) |>
  pivot_wider(id_cols = c(HouseID, ac.type, Post_response_Q25), names_from = Survey, values_from = threat_score) |> 
  mutate(score_diff = `Post-Intervention` - `Pre-Intervention`) |> 
 filter(!is.na(score_diff))


jitter_pos <- position_jitter(width = 0.3, height = 0, seed = 42)

ggplot(threat_behavior_score_Q25_diff, aes(x = Post_response_Q25, y = score_diff, color = Post_response_Q25)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(position = jitter_pos, aes(shape = ac.type)) +
  geom_label_repel(
    aes(label = HouseID),
    position = jitter_pos,
    size = 3,
    min.segment.length = .6,  
    segment.color = "grey70", 
    color = 'grey70',
    box.padding = 0.4,
    show.legend = FALSE,
    alpha=0.7
  ) +
  labs(
    x = "Change in behavior in post-intervention survey due to outdoor air pollution (Q25)",
    y = "Difference in threat score (post - pre)",
    color = "Home ID",
    shape = "AC Type"
  ) +
  geom_signif(
    comparisons = list(c('Change', 'No Change')),
    map_signif_level = function(p) sprintf("p = %.2f", p),
    test = 't.test',
    color = 'black',
    vjust = 0,
    margin_top = 0.1
  ) +
  scale_color_manual(values = okabe_ito[5:6], name = "Behavior") +
  guides(color = "none") +    
  theme_bw()


ggsave("./Graphics/diff_threat_by_behavior.tiff",
       width = 170, height = 120,
       units = "mm",
       dpi = 300,
       compression = "lzw")
```

Figure 4 for Q25. Knowledge difference by Q25 behavior change group

```{r}
# overall knowledge

names(threat_behavior_score_Q25)

set.seed(123) # for reproducibility of jitter
ggplot(threat_behavior_score_Q25, aes(x = Q25, y = knowledge_score, color=Q25)) +
  geom_boxplot(data = threat_behavior_score_Q25 |>
                 filter(!(Survey == "Pre-Intervention" & Q25 == "No Change")),
               outlier.shape = NA)+
   geom_jitter(width=0.3,height=0, aes(shape = ac.type))+
  facet_wrap(~Survey, labeller = labeller(Survey = c("Pre-Intervention"= "Pre-Intervention (n=14)", "Post-Intervention" = "Post-Intervention (n=15)"))) +
    geom_signif(
    comparisons = list(c('Change', 'No Change')),
    map_signif_level = function(p) sprintf("p = %.3f", p),
    test = 't.test',
    color = 'black',
    vjust = 0,
    margin_top = 0.1
  ) +
  labs(
    x = "Change in Behavior due to Outdoor Air Pollution (Q25)",
    y = "Knowledge Score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  #scale_color_grey()+
 scale_color_manual(values = okabe_ito[5:6], name = "House Type") +
    guides(color = "none") + 
  theme_bw()


ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/knowledge_behavior_plot.jpeg")

```


Figure 5 for Q25: Compare threat perception and air quality scores, broken out by ac.type

```{r}

threat_behavior_score_Q25_3 <- threat_behavior_score_Q25_2 |> 
  filter(Survey == "Post-Intervention") |> 
  select(HouseID, ac.type, Post_response_Q25, knowledge_score, mean_IO_PM_Summer, mean_IO_O3_Summer) |> 
  pivot_longer(cols = c(mean_IO_PM_Summer, mean_IO_O3_Summer), names_to = "Pollutant", values_to = "AQ_score") |> 
  mutate(Pollutant = recode(Pollutant, "mean_IO_PM_Summer" = "PM2.5", "mean_IO_O3_Summer" = "O3"))



set.seed(123)
ggplot(threat_behavior_score_Q25_3, aes(x = Post_response_Q25, y = AQ_score, color = Post_response_Q25)) +
  geom_boxplot(data = threat_behavior_score_Q25_3 |>
                 filter(!(Post_response_Q25 == "No Change" & ac.type == "EC")),
               outlier.shape = NA) +
  geom_jitter(width = 0.3, height = 0, aes(shape = ac.type)) +
    geom_signif(
    comparisons = list(c('Change', 'No Change')),
    map_signif_level = function(p) sprintf("p = %.3f", p),
    test = 't.test',
    color = 'black',
    vjust = 0,
    margin_top = 0.1
  ) +
  facet_grid(Pollutant~ac.type,scales="free_y") +
  labs(
    x = "Change in Behavior due to Outdoor Air Pollution (Q25)",
    y = "Indoor/Outdoor Ratio",
      shape = "House Type"
  ) +
  scale_color_manual(values = okabe_ito[5:6], name = "House Type") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))+
  guides(color = "none") + 
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/IO_behavior_plot_Q25.jpeg")

```

Figure 1 for Q29

```{r}

threat_behavior_score_Q29 <- threat_behavior_score |>
  filter(!is.na(Q29))

set.seed(123)
ggplot(threat_behavior_score_Q29, aes(x = Q29, y = threat_score, color = Q29)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.3, height = 0, aes(shape = ac.type)) +
    geom_signif(
    comparisons = list(c('Change', 'No Change')),
    map_signif_level = function(p) sprintf("p = %.3f", p),
    test = 't.test',
    color = 'black',
    vjust = 0,
    margin_top = 0.1
  ) +
  facet_wrap(~Survey) +
  labs(
    x = "Changes made to home to improve air quality (Q29)",
    y = "Total threat score",
      shape = "House Type"
  ) +
  scale_color_manual(values = okabe_ito[7:8], name = "House Type") +
  guides(color = "none") + 
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/threat_behavior_plot_Q29.jpeg")

```



Figure 2 for Q29 
Threat score by behavior change group, with lines connecting the same HouseID across surveys.

```{r}

threat_behavior_score_Q29 <- threat_behavior_score |> 
  filter(!is.na(Q29)) |> 
  select(HouseID, Survey, ac.type, Q29, sample, threat_score,knowledge_score, mean_IO_PM_Summer, mean_IO_O3_Summer) 

## Create a dataframe that has the post-intervention behavior responses for Q29, and merge that with the threat scores to get a dataframe that has the pre- and post- threat scores and the post-intervention responses for Q29.

behavior_Q29_post <- threat_behavior_score |>
  filter(Survey == "Post-Intervention") |>
  select(HouseID, Q29) |> 
  mutate(Post_response_Q29 = case_when(HouseID == "H29" ~ "No Change", 
         TRUE ~ Q29)) |> ## impute the response for H29 since they only have a pre-intervention survey and they said they made no changes to their home in the pre-intervention survey
  select(-Q29) |> 
  filter(!is.na(Post_response_Q29))

## join this with the threat scores, and filter to only include rows that have a post-intervention response for Q29 

threat_behavior_score_Q29_2 <- threat_behavior_score |> 
  left_join(behavior_Q29_post, by = "HouseID") 

names(threat_behavior_score_Q29_2)

## geom_point and geom_line
ggplot(threat_behavior_score_Q29_2, aes(x = Survey, y = threat_score)) +
    geom_point(width=0.3,height=0, aes(shape = ac.type, color = Q29))+
   geom_line(aes(group = HouseID), color = "grey80", alpha = 0.5) +  # add lines connecting points for the same HouseID
  facet_wrap(~Post_response_Q29, labeller = labeller(Post_response_Q29 = c("Change" = "Change Home in Post-Intervention", "No Change" = "No Change in Home in Post-Intervention"))) +
  labs(
    x = "Survey",
    y = "Threat score",
    color = "Home Type",
    shape = "AC Type"
  ) +
    geom_label_repel(
    data = threat_behavior_score_Q29_2 |>
      filter(Survey == "Post-Intervention"),
    aes(label = HouseID),
    size = 3,
    min.segment.length = .6,
    segment.color = "grey70",
    color = 'grey70',
    box.padding = 0.4,
    show.legend = FALSE,
    alpha=0.7
  ) +
 scale_color_manual(values = okabe_ito[7:8], name = "Behavior") +
  theme_bw()

  ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/threat_diff_by_behavior_lines_Q29.jpeg")


```

Figure 3 for Question 29

```{r}
library(ggrepel)

threat_behavior_score_Q29_diff <- threat_behavior_score_Q29_2 |> 
  select(HouseID, ac.type, Post_response_Q29, Survey, threat_score) |>
  pivot_wider(id_cols = c(HouseID, ac.type, Post_response_Q29), names_from = Survey, values_from = threat_score) |> 
  mutate(score_diff = `Post-Intervention` - `Pre-Intervention`) |> 
 filter(!is.na(score_diff))


jitter_pos <- position_jitter(width = 0.3, height = 0, seed = 42)

ggplot(threat_behavior_score_Q29_diff, aes(x = Post_response_Q29, y = score_diff, color = Post_response_Q29)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(position = jitter_pos, aes(shape = ac.type)) +
  geom_label_repel(
    aes(label = HouseID),
    position = jitter_pos,
    size = 3,
    min.segment.length = .6,  
    segment.color = "grey70", 
    color = 'grey70',
    box.padding = 0.4,
    show.legend = FALSE,
    alpha=0.7
  ) +
  labs(
    x = "Change in home to improve indoor air in post-intervention survey  (Q29)",
    y = "Difference in threat score (post - pre)",
    color = "Home ID",
    shape = "AC Type"
  ) +
  geom_signif(
    comparisons = list(c('Change', 'No Change')),
    map_signif_level = function(p) sprintf("p = %.2f", p),
    test = 't.test',
    color = 'black',
    vjust = 0,
    margin_top = 0.1
  ) +
  scale_color_manual(values = okabe_ito[7:8], name = "Behavior") +
  guides(color = "none") +    
  theme_bw()


ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/diff_threat_by_behavior_Q29.jpeg")


```






Figure 4 for Q29

```{r}

names(threat_behavior_score_Q29)

set.seed(123) # for reproducibility of jitter
ggplot(threat_behavior_score_Q29, aes(x = Q29, y = knowledge_score, color=Q29)) +
  geom_boxplot(data = threat_behavior_score_Q29 , outlier.shape = NA)+
   geom_jitter(width=0.3,height=0, aes(shape = ac.type))+
  facet_wrap(~Survey, labeller = labeller(Survey = c("Pre-Intervention"= "Pre-Intervention (n=14)", "Post-Intervention" = "Post-Intervention (n=15)"))) +
    geom_signif(
    comparisons = list(c('Change', 'No Change')),
    map_signif_level = function(p) sprintf("p = %.3f", p),
    test = 't.test',
    color = 'black',
    vjust = 0,
    margin_top = 0.1
  ) +
  labs(
    x = "Change in Behavior due to Outdoor Air Quality (Q29)",
    y = "Knowledge Score",
    color = "Home Type",
    shape = "AC Type"
  ) +
  #scale_color_grey()+
 scale_color_manual(values = okabe_ito[7:8], name = "House Type") +
    guides(color = "none") + 
  theme_bw()


ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/knowledge_behavior_plot_Q29.jpeg")
```

Figure 5 for Q29: Compare threat perception and air quality scores, broken out by ac.type

```{r}

threat_behavior_score_Q29_3 <- threat_behavior_score_Q29_2 |> 
  filter(Survey == "Post-Intervention") |> 
  select(HouseID, ac.type, Post_response_Q29, knowledge_score, mean_IO_PM_Summer, mean_IO_O3_Summer) |> 
  pivot_longer(cols = c(mean_IO_PM_Summer, mean_IO_O3_Summer), names_to = "Pollutant", values_to = "AQ_score") |> 
  mutate(Pollutant = recode(Pollutant, "mean_IO_PM_Summer" = "PM2.5", "mean_IO_O3_Summer" = "O3"))


set.seed(123)
ggplot(threat_behavior_score_Q29_3, aes(x = Post_response_Q29, y = AQ_score, color = Post_response_Q29)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.3, height = 0, aes(shape = ac.type)) +
    geom_signif(
    comparisons = list(c('Change', 'No Change')),
    map_signif_level = function(p) sprintf("p = %.3f", p),
    test = 't.test',
    color = 'black',
    vjust = 0,
    margin_top = 0.1
  ) +
  facet_grid(Pollutant~ac.type,scales="free_y") +
  labs(
    x = "Changes made to home to improve air quality (Q29)",
    y = "Indoor/Outdoor Ratio",
      shape = "House Type"
  ) +
  scale_color_manual(values = okabe_ito[7:8], name = "House Type") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))+
  guides(color = "none") + 
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/IO_behavior_plot_Q29.jpeg")






```






## Risk perception vs. PM2.5 and O3 air quality scores

```{r}
## Compare risk perception and air quality scores, broken out by ac.type

names(threat_behavior_score_Q25 )

## try PM specific threat...

pm_threat_labels <- threat_behavior_score_Q25 |>
  filter(!is.na(PM2.5_threat_score), !is.na(mean_IO_PM_Summer)) |>
  group_by(ac.type, Survey) |>
  summarise(
    r_sq = summary(lm(PM2.5_threat_score ~ mean_IO_PM_Summer))$r.squared,
    p_val = summary(lm(PM2.5_threat_score ~ mean_IO_PM_Summer))$coefficients[2, 4],
    .groups = "drop"
  ) |>
  mutate(label = if_else(p_val < 0.001,
                         sprintf("R² = %.3f, p < 0.001", r_sq),
                         sprintf("R² = %.3f, p = %.3f", r_sq, p_val)))

ggplot(threat_behavior_score_Q25, aes(y = PM2.5_threat_score, x = mean_IO_PM_Summer)) +
   geom_point(aes(shape = ac.type, color = ac.type))+
   geom_smooth(method = "lm", se = TRUE, color = "black") +
  facet_grid(ac.type~Survey, scales="free_y") +
  geom_text(data = pm_threat_labels, aes(label = label),
            x = Inf, y = Inf, hjust = 1.05, vjust = 1.5,
            size = 3, fontface = "italic", inherit.aes = FALSE) +
  labs(
    y = "PM2.5 Threat",
    x = "PM2.5 Indoor/Outdoor Ratio",
    color = "Home Type",
    shape = "AC Type"
  ) +
 ylim(0.2,1.0) +
 xlim(0.2,1.4) +
 scale_y_continuous(breaks = seq(0.2, 1.0, by = 0.2)) +
scale_x_continuous(breaks = seq(0.2, 1.4, by = 0.2)) +
 scale_color_manual(values = okabe_ito, name = "House Type") +
 scale_shape_manual(values = c(16, 17), name = "House Type") +
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/PM2.5_vs_threat_lm.jpeg")


```



```{r}
## threat vs Ozone

o3_threat_labels <- threat_behavior_score_Q25 |>
  filter(!is.na(O3_threat_score), !is.na(mean_IO_O3_Summer)) |>
  group_by(ac.type, Survey) |>
  summarise(
    r_sq = summary(lm(O3_threat_score ~ mean_IO_O3_Summer))$r.squared,
    p_val = summary(lm(O3_threat_score ~ mean_IO_O3_Summer))$coefficients[2, 4],
    .groups = "drop"
  ) |>
  mutate(label = if_else(p_val < 0.001,
                         sprintf("R² = %.3f, p < 0.001", r_sq),
                         sprintf("R² = %.3f, p = %.3f", r_sq, p_val)))

ggplot(threat_behavior_score_Q25, aes(y = O3_threat_score, x = mean_IO_O3_Summer)) +
   geom_point(aes(shape = ac.type, color = ac.type))+
   geom_smooth(method = "lm", se = TRUE, color = "black") +
  facet_grid(ac.type~Survey, scales="free_y") +
  geom_text(data = o3_threat_labels, aes(label = label),
            x = Inf, y = Inf, hjust = 1.05, vjust = 1.5,
            size = 3, fontface = "italic", inherit.aes = FALSE) +
  labs(
    y = "O3 Threat",
    x = "O3 Indoor/Outdoor Ratio",
    color = "Home Type",
    shape = "AC Type"
  ) +
 ylim(0.2,1.0) +
 xlim(0.2,1.4) +
 scale_y_continuous(breaks = seq(0.2, 1.0, by = 0.2)) +
scale_x_continuous(breaks = seq(0, 0.8, by = 0.2)) +
 scale_color_manual(values = okabe_ito, name = "House Type") +
 scale_shape_manual(values = c(16, 17), name = "House Type") +
  theme_bw()

ggsave(width = 7, height = 5, dpi = 300, units = "in", bg = "white", filename = "./Graphics/O3_vs_threat_lm.jpeg")



```
