
```{r}
library(tidyverse)
library(coin)
library(knitr)
library(kableExtra)
library(VIM)
library(ggrepel)
```

```{r}
df_raw <- read_csv("./Processed Data/survey_aq_data.csv") |>
  mutate(Score_mod = case_when(
    QuestionID %in% c('Q01','Q02','Q03','Q04','Q05','Q06','Q07','Q08') &
      HouseID == "H29" & Survey == "Post_Intervention" ~ NA,
    TRUE ~ Score_mod
  ))

fa_df <- df_raw %>%
  select(HouseID, Survey, QuestionID, Score_mod) %>%
  filter(QuestionID %in% paste0("Q", sprintf("%02d", 9:22))) %>%
  pivot_wider(id_cols = c(HouseID, Survey), names_from = QuestionID, values_from = Score_mod) %>%
  filter(HouseID != "H29")

fa_df_imputed <- kNN(fa_df %>% dplyr::select(-c(HouseID, Survey))) %>%
  select(1:(ncol(fa_df)-2)) %>%
  mutate(HouseID = fa_df$HouseID,
         Survey = fa_df$Survey)

groups <- df_raw %>%
  filter(!QuestionID %in% c("Q23", "Q24")) %>% # duplicate quesitons
  select(QuestionID, Construct) %>%
  distinct(.keep_all = TRUE) %>%
  group_by(Construct) %>%
  summarize(QuestionIDs = list(QuestionID)) %>%
  ungroup()

sevo3_qs <- groups %>% filter(Construct == "Perceived Severity (O3)") %>% pull(QuestionIDs)
sevpm_qs <- groups %>% filter(Construct == "Perceived Severity (PM2.5)") %>% pull(QuestionIDs)
suso3_qs <- groups %>% filter(Construct == "Perceived Susceptibility (O3)") %>% pull(QuestionIDs)
suspm_qs <- groups %>% filter(Construct == "Perceived Susceptibility (PM2.5)") %>%
  pull(QuestionIDs)
```

This next function takes get_score_analysis and changes it to be able to run the wilcoxon test, and also adding adjusted P-values and unadjusted p-values. Also using Holme Testing
```{r}
wilcoxon_score_analysis <- function(qs, construct_name) {

  total_possible <- length(qs)*5

  test2_df <- fa_df_imputed %>%
    select(HouseID, Survey, all_of(qs)) %>%
    mutate(total_score = rowSums(across(all_of(qs)))) %>%
    select(HouseID, Survey, total_score) %>%
    pivot_wider(id_cols = HouseID,
                names_from = Survey,
                values_from = total_score) %>%
    mutate(Post_Intervention = Post_Intervention/total_possible,
           Pre_Intervention = Pre_Intervention/total_possible,
      difference = Post_Intervention - Pre_Intervention)

  # wilcoxsign_test is coin's paired (signed-rank) test: it takes the two
  # paired columns directly, no long-format value/group reshaping needed.
  test <- wilcoxsign_test(Post_Intervention ~ Pre_Intervention,
                           data = test2_df,
                           distribution = "exact")

  # conf.int = TRUE requires a coin version that supports it for
  # wilcoxsign_test; fall back to base wilcox.test's Hodges-Lehmann CI
  # (same estimand) if the installed coin version doesn't support it.
  ci_est <- tryCatch({
    test_ci <- wilcoxsign_test(Post_Intervention ~ Pre_Intervention,
                                data = test2_df,
                                distribution = "exact",
                                conf.int = TRUE)
    ci_out <- confint(test_ci)
    list(estimate = unname(ci_out$estimate), ci = ci_out$conf.int)
  }, error = function(e) {
    wt <- wilcox.test(test2_df$Post_Intervention, test2_df$Pre_Intervention,
                       paired = TRUE, conf.int = TRUE, exact = TRUE)
    list(estimate = unname(wt$estimate), ci = wt$conf.int)
  })

  # coin test objects are S4 - use statistic()/pvalue(), not $statistic/$p.value.
  list(
    Construct = construct_name,
    data = test2_df,
    n = sum(!is.na(test2_df$difference)),
    pre_score = mean(test2_df$Pre_Intervention, na.rm = TRUE),
    post_score = mean(test2_df$Post_Intervention, na.rm = TRUE),
    z_stat = coin::statistic(test),
    p_value = coin::pvalue(test),
    median_diff = median(test2_df$difference, na.rm = TRUE),
    estimate = ci_est$estimate,
    ci = ci_est$ci
  )
}

construct_qs <- list(
  "Perceived Severity (O3)" = sevo3_qs[[1]],
  "Perceived Susceptibility (O3)" = suso3_qs[[1]],
  "Perceived Threat (O3)" = c(sevo3_qs[[1]], suso3_qs[[1]]),
  "Perceived Severity (PM2.5)" = sevpm_qs[[1]],
  "Perceived Susceptibility (PM2.5)" = suspm_qs[[1]],
  "Perceived Threat (PM2.5)" = c(sevpm_qs[[1]], suspm_qs[[1]])
)

results <- lapply(names(construct_qs), function(con) {
  wilcoxon_score_analysis(construct_qs[[con]], con)
})

raw_p <- sapply(results, function(x) x$p_value)

# Holm correction applied separately within each pollutant, not across all 6
# constructs together - ave() splits raw_p by pollutant, runs p.adjust on
# each subset, then recombines in the original construct order.
pollutant <- case_when(
  str_detect(sapply(results, function(x) x$Construct), "O3") ~ "O3",
  str_detect(sapply(results, function(x) x$Construct), "PM2.5") ~ "PM2.5",
  TRUE ~ NA_character_
)
adj_p <- ave(raw_p, pollutant, FUN = function(p) p.adjust(p, method = "holm"))

summary_table <- bind_rows(lapply(seq_along(results), function(i) {
  x <- results[[i]]
  data.frame(
    Construct = x$Construct,
    N = x$n,
    `Pre Survey Score` = round(x$pre_score, 2),
    `Post Survey Score` = round(x$post_score, 2),
    `Median Difference` = round(x$median_diff, 2),
    `Hodges-Lehmann Estimate` = round(x$estimate, 2),
    `Z-stat` = round(x$z_stat, 2),
    `P-value` = round(raw_p[i], 3),
    `Adj. P-value` = round(adj_p[i], 3),
    `95% CI` = paste0("(", round(x$ci[1], 2), ", ", round(x$ci[2], 2), ")"),
    Pollutant = pollutant[i],
    check.names = FALSE
  )
}))

summary_table <- summary_table %>%
  arrange(Pollutant, Construct)

write_csv(summary_table |> select(-Pollutant),'./Processed Data/wilcox_diff_risk_constructs.csv')

# pack_rows needs consecutive run-lengths per group, in the order rows
# appear after arrange() above (O3 rows first, then PM2.5 rows)
group_index <- rle(summary_table$Pollutant)
group_index <- setNames(group_index$lengths, group_index$values)

tbl_grouped <- summary_table %>%
  select(-Pollutant) %>%
  kable(row.names = FALSE,
        booktabs = TRUE,
        caption = "Wilcoxon Signed-Rank Tests by Pollutant and Construct") %>%
  kable_styling(latex_options = "hold_position", font_size = 9, full_width = FALSE) %>%
  pack_rows(index = group_index)

tbl_grouped
```

Fig 2 (Wilcoxon version): same layout as the t-test bar chart, but plotting each construct's Hodges-Lehmann estimate of the pre/post shift with its Wilcoxon-based confidence interval, taken directly from `results` (`wilcoxon_score_analysis` output) instead of a t-test mean/CI.
```{r}
okabe_ito <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
               "#0072B2", "#D55E00", "#CC79A7", "#000000",
               "#332288", "#117733", "#44AA99", "#88CCEE",
               "#DDCC77", "#882255")

risk_graphic_df <- bind_rows(lapply(results, function(x) {
  data.frame(
    Construct = x$Construct,
    Estimate = x$estimate,
    ci_lower = x$ci[1],
    ci_upper = x$ci[2]
  )
}))

risk_graphic_df$Construct <- factor(risk_graphic_df$Construct,
  levels = c("Perceived Susceptibility (O3)", "Perceived Susceptibility (PM2.5)",
             "Perceived Severity (O3)", "Perceived Severity (PM2.5)",
             "Perceived Threat (O3)", "Perceived Threat (PM2.5)"), ordered = TRUE)

construct_diff_wilcox_plt <- ggplot(risk_graphic_df, aes(y = Construct, x = Estimate, fill = Construct)) +
  geom_col(width = 0.6) +
  geom_errorbar(
    aes(xmin = ci_lower, xmax = ci_upper),
    width = 0.15,
    linewidth = .5
  ) +
  geom_label(aes(y = Construct, x = Estimate, label = round(Estimate, digits = 2)),
             fill = 'white', size = 3) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.5) +
  labs(
    x = "Score Difference",
    y = "Construct"
  ) +
  theme_bw() +
  scale_fill_manual(values = okabe_ito[9:14], name = "House Type") +
  theme(legend.position = 'none',
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 10)) +
  scale_y_discrete(limits = rev)

construct_diff_wilcox_plt

ggsave("./Graphics/Fig2_construct_difference_wilcox_plot.tiff", construct_diff_wilcox_plt,
       dpi = 300, units = 'in', width = 4, height = 4)
```

### Knowledge Scores

Wilcoxon version of the knowledge-score analysis (analysis.qmd's `t.test`-based cell): paired Wilcoxon signed-rank tests (via `wilcoxsign_test`, same approach as `wilcoxon_score_analysis` above) on pre/post knowledge score differences by pollutant, with Holm-adjusted p-values across the three tests to match the convention used for the risk-construct table.
```{r}
# Changes single response questions from -1 to 0
qs_not_to_change <- c("Q04", "Q08")

# overall knowledge
knowledge_df <- df_raw %>%
  filter(Construct_general == "Knowledge") %>%
  select(HouseID, Survey, QuestionID, Score_mod) %>%
  mutate(Score_mod = case_when(!QuestionID %in% qs_not_to_change & Score_mod == -1 ~ 0,
                               TRUE ~ Score_mod)) %>%
  group_by(HouseID, Survey) %>%
  summarize(score = sum(Score_mod)) %>%
  ungroup() %>%
  pivot_wider(id_cols = HouseID,
              names_from = Survey,
              values_from = score) %>%
  mutate(difference = Post_Intervention - Pre_Intervention)

knowledgeo3_qs <- groups %>% filter(Construct == "Knowledge (O3)") %>% pull(QuestionIDs)
knowledgepm_qs <- groups %>% filter(Construct == "Knowledge (PM2.5)") %>% pull(QuestionIDs)

# o3 knowledge
knowledge03_df <- df_raw %>%
  select(HouseID, Survey, QuestionID, Score_mod) %>%
  mutate(Score_mod = case_when(!QuestionID %in% qs_not_to_change & Score_mod == -1 ~ 0,
                               TRUE ~ Score_mod)) %>%
  filter(QuestionID %in% knowledgeo3_qs[[1]]) %>%
  group_by(HouseID, Survey) %>%
  summarize(score = sum(Score_mod)) %>%
  ungroup() %>%
  pivot_wider(id_cols = HouseID,
              names_from = Survey,
              values_from = score) %>%
  mutate(difference = Post_Intervention - Pre_Intervention)

# pm2.5 knowledge
knowledgepm_df <- df_raw %>%
  select(HouseID, Survey, QuestionID, Score_mod) %>%
  mutate(Score_mod = case_when(!QuestionID %in% qs_not_to_change & Score_mod == -1 ~ 0,
                               TRUE ~ Score_mod)) %>%
  filter(QuestionID %in% knowledgepm_qs[[1]]) %>%
  group_by(HouseID, Survey) %>%
  summarize(score = sum(Score_mod)) %>%
  ungroup() %>%
  pivot_wider(id_cols = HouseID,
              names_from = Survey,
              values_from = score) %>%
  mutate(difference = Post_Intervention - Pre_Intervention)

# Paired Wilcoxon signed-rank test on a Pre/Post/difference df, mirroring
# wilcoxon_score_analysis() above but without the total_possible normalization
# (knowledge scores here are raw summed points, same as the t-test version).
wilcoxon_knowledge_test <- function(df) {
  test <- wilcoxsign_test(Post_Intervention ~ Pre_Intervention,
                           data = df,
                           distribution = "exact")

  ci_est <- tryCatch({
    test_ci <- wilcoxsign_test(Post_Intervention ~ Pre_Intervention,
                                data = df,
                                distribution = "exact",
                                conf.int = TRUE)
    ci_out <- confint(test_ci)
    list(estimate = unname(ci_out$estimate), ci = ci_out$conf.int)
  }, error = function(e) {
    wt <- wilcox.test(df$Post_Intervention, df$Pre_Intervention,
                       paired = TRUE, conf.int = TRUE, exact = TRUE)
    list(estimate = unname(wt$estimate), ci = wt$conf.int)
  })

  list(
    n = sum(!is.na(df$difference)),
    pre_score = mean(df$Pre_Intervention, na.rm = TRUE),
    post_score = mean(df$Post_Intervention, na.rm = TRUE),
    z_stat = coin::statistic(test),
    p_value = coin::pvalue(test),
    median_diff = median(df$difference, na.rm = TRUE),
    estimate = ci_est$estimate,
    ci = ci_est$ci
  )
}

knowledge_test <- wilcoxon_knowledge_test(knowledge_df)
knowledge_o3test <- wilcoxon_knowledge_test(knowledge03_df)
knowledge_pmtest <- wilcoxon_knowledge_test(knowledgepm_df)

knowledge_raw_p <- c(knowledge_o3test$p_value, knowledge_pmtest$p_value, knowledge_test$p_value)
knowledge_adj_p <- p.adjust(knowledge_raw_p, method = "holm")

knowledge_table_df <- data.frame(
  Pollutant = c("O3", "PM2.5", "Total"),

  N = c(knowledge_o3test$n, knowledge_pmtest$n, knowledge_test$n),

  `Pre Survey Score` = round(c(knowledge_o3test$pre_score, knowledge_pmtest$pre_score, knowledge_test$pre_score), 2),

  `Post Survey Score` = round(c(knowledge_o3test$post_score, knowledge_pmtest$post_score, knowledge_test$post_score), 2),

  `Median Difference` = round(c(knowledge_o3test$median_diff, knowledge_pmtest$median_diff, knowledge_test$median_diff), 2),

  `Hodges-Lehmann Estimate` = round(c(knowledge_o3test$estimate, knowledge_pmtest$estimate, knowledge_test$estimate), 2),

  `Z-stat` = round(c(knowledge_o3test$z_stat, knowledge_pmtest$z_stat, knowledge_test$z_stat), 2),

  `P-value` = round(knowledge_raw_p, 3),

  `Adj. P-value` = round(knowledge_adj_p, 3),

  `95% CI` = c(
    paste0("(", round(knowledge_o3test$ci[1], 2), ", ", round(knowledge_o3test$ci[2], 2), ")"),
    paste0("(", round(knowledge_pmtest$ci[1], 2), ", ", round(knowledge_pmtest$ci[2], 2), ")"),
    paste0("(", round(knowledge_test$ci[1], 2), ", ", round(knowledge_test$ci[2], 2), ")")
  ),

  check.names = FALSE
)

options(knitr.kable.NA = '--')
tbl2_wilcox <- knowledge_table_df %>%
  kable(
    row.names = FALSE,
    digits = 4,
    booktabs = TRUE,
    caption = "Wilcoxon Signed-Rank Tests of Pre- vs Post-Intervention Knowledge Differences by Pollutant"
  ) %>%
  kable_styling(latex_options = "hold_position",
                font_size = 9,
                full_width = FALSE) %>%
  row_spec(0, extra_css = "font-family: Arial;")
tbl2_wilcox

write_csv(knowledge_table_df, './Processed Data/wilcox_diff_knowledge.csv')

knowledge_graph_df <- tibble(
  Pollutant = c("O3", "PM2.5", "Total"),
  Estimate = c(knowledge_o3test$estimate, knowledge_pmtest$estimate, knowledge_test$estimate),
  ci_lower = c(knowledge_o3test$ci[1], knowledge_pmtest$ci[1], knowledge_test$ci[1]),
  ci_upper = c(knowledge_o3test$ci[2], knowledge_pmtest$ci[2], knowledge_test$ci[2]),
)

knowledge_dif_wilcox_plt <- ggplot(knowledge_graph_df, aes(y = Pollutant, x = Estimate, fill = Pollutant)) +
  geom_col(width = 0.6) +
  geom_errorbar(
    aes(xmin = ci_lower, xmax = ci_upper),
    width = 0.15,
    linewidth = .5
  ) +
  geom_label(aes(y = Pollutant, x = Estimate, label = round(Estimate, digits = 2)), fill = 'white', size = 3) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.5) +
  labs(
    x = "Knowledge Score Difference",
    y = "Pollutant"
  ) +
  theme_bw() +
  scale_fill_manual(values = okabe_ito[3:5], name = "House Type") +
  theme(legend.position = 'none',
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 10)) +
  scale_y_discrete(limits = rev)

knowledge_dif_wilcox_plt

ggsave("./Graphics/Fig3_knowledge_difference_wilcox_plot.tiff", knowledge_dif_wilcox_plt,
       dpi = 300, units = 'in', width = 3, height = 3)
```

### Difference in Threat vs. Order of Indoor/Outdoor Ratio

Ported from analysis_ds.qmd. Reuses the O3/PM2.5 "Perceived Threat" pre/post differences already computed in `results` above (same normalized score, so no need to recompute from scratch) and joins in each house's AC type and mean Indoor/Outdoor ratio. Instead of the hardcoded p-value text labels in the original, the Spearman correlation is computed directly from the data so the label can't go stale.
```{r}
metadata <- df_raw %>%
  filter(QuestionID == "Q25", Survey == "Pre_Intervention") %>%
  select(HouseID, ac.type, mean_IO_PM_Summer, mean_IO_O3_Summer)

get_construct_diff <- function(construct_name) {
  results[[which(sapply(results, `[[`, "Construct") == construct_name)]]$data %>%
    select(HouseID, score = difference)
}

threat_diff_by_pollutant <- bind_rows(
  get_construct_diff("Perceived Threat (O3)") %>% mutate(pollutant = "O3"),
  get_construct_diff("Perceived Threat (PM2.5)") %>% mutate(pollutant = "PM2.5")
) %>%
  left_join(metadata, by = "HouseID") %>%
  mutate(IO_ratio = if_else(pollutant == "O3", mean_IO_O3_Summer, mean_IO_PM_Summer)) %>%
  select(HouseID, ac.type, pollutant, score, IO_ratio)

threat_diff_by_pollutant_order <- threat_diff_by_pollutant %>%
  filter(!is.na(score)) %>%
  group_by(pollutant) %>%
  mutate(IO_order = dense_rank(IO_ratio)) %>%
  ungroup()

# Bootstrap percentile CI for Spearman's rho (nonparametric, consistent with
# the rank-based tests used elsewhere in this document) since cor.test()
# doesn't provide a CI for method = "spearman".
spearman_stats <- threat_diff_by_pollutant_order %>%
  filter(!is.na(IO_ratio)) %>%
  group_split(pollutant) %>%
  map_dfr(function(d) {
    ct <- cor.test(d$score, d$IO_ratio, method = "spearman", exact = FALSE)
    boot_fn <- function(data, indices) {
      cor(data$score[indices], data$IO_ratio[indices], method = "spearman")
    }
    set.seed(3) # for reproducibility

    # ci for bootstrap percentile interval. Bootstrapping keeps everything nonparametric / rank-based, so that it stays consistent with the Wilcoxon test methodologies
    b <- boot::boot(d, boot_fn, R = 2000)
    ci <- boot::boot.ci(b, type = "perc")$percent[4:5]
    tibble(
      pollutant = unique(d$pollutant),
      rho = unname(ct$estimate),
      p_val = ct$p.value,
      ci_lower = ci[1],
      ci_upper = ci[2]
    )
  })

spearman_label <- spearman_stats %>%
  mutate(label = paste0(
    "Spearman's rho = ", round(rho, 2),
    " (95% CI: ", round(ci_lower, 2), ", ", round(ci_upper, 2), "), ",
    "p = ", round(p_val, 3)
  ))

set.seed(3)
IO_vs_diff_threat_order_plt <- ggplot(threat_diff_by_pollutant_order, aes(y = score, x = IO_order)) +
  geom_point(aes(shape = ac.type, color = ac.type)) +
  facet_grid(. ~ pollutant, scales = "free_y") +
  geom_text(data = spearman_label, aes(label = label),
            x = Inf, y = Inf, hjust = 1.05, vjust = 1.5,
            size = 3, fontface = "italic", inherit.aes = FALSE) +
  geom_label_repel(
    data = threat_diff_by_pollutant_order %>%
      filter(HouseID %in% c('H02', 'H05')),
    aes(label = HouseID),
    size = 3,
    nudge_x = -1,
    min.segment.length = .2,
    segment.color = "grey70",
    color = 'grey70',
    box.padding = 0.4,
    show.legend = FALSE,
    alpha = 0.7,
    seed = 5
  ) +
  labs(
    y = "Difference in Threat (post - pre)",
    x = "Rank in Indoor/Outdoor Ratio",
    color = "Home Type",
    shape = "Home Type"
  ) +
  theme_bw() +
  theme(legend.position = "bottom") +
  expand_limits(y = 0.11) +
  scale_x_continuous(limits = c(0, 16), breaks = seq(0, 16, by = 4)) +
  scale_color_manual(values = okabe_ito, name = "House Type") +
  scale_shape_manual(values = c(16, 17), name = "House Type")

IO_vs_diff_threat_order_plt

ggsave(width = 7, height = 4, dpi = 300, units = "in", bg = "white",
       filename = "./Graphics/IO_vs_diff_threat_order.tiff")
```

The above was run with KNN imputations, and now we need to take a look at the data and the results without those houses 6 and 11.

Without houses and KNN imputation for the supplementary document:
```{r}
# Overwrite the fa_df_imputed so that it doesn't do the KNN imputation
fa_df_imputed <- fa_df

results_no_impute <- lapply(names(construct_qs), function(con) {
  wilcoxon_score_analysis(construct_qs[[con]], con)
})

raw_p_ni <- sapply(results_no_impute, function(x) x$p_value)

pollutant_ni <- case_when(
  str_detect(sapply(results_no_impute, function(x) x$Construct), "O3") ~ "O3",
  str_detect(sapply(results_no_impute, function(x) x$Construct), "PM2.5") ~ "PM2.5",
  TRUE ~ NA_character_
)
adj_p_ni <- ave(raw_p_ni, pollutant_ni, FUN = function(p) p.adjust(p, method = "holm"))

summary_table_no_impute <- bind_rows(lapply(seq_along(results_no_impute), function(i) {
  x <- results_no_impute[[i]]
  data.frame(
    Construct = x$Construct,
    N = x$n,
    `Pre Survey Score` = round(x$pre_score, 2),
    `Post Survey Score` = round(x$post_score, 2),
    `Median Difference` = round(x$median_diff, 2),
    `Hodges-Lehmann Estimate` = round(x$estimate, 2),
    `Z-stat` = round(x$z_stat, 2),
    `P-value` = round(raw_p_ni[i], 3),
    `Adj. P-value` = round(adj_p_ni[i], 3),
    `95% CI` = paste0("(", round(x$ci[1], 2), ", ", round(x$ci[2], 2), ")"),
    Pollutant = pollutant_ni[i],
    check.names = FALSE
  )
})) %>%
  arrange(Pollutant, Construct)

write_csv(summary_table_no_impute |> select(-Pollutant),'./Processed Data/wilcox_diff_risk_noKNN_constructs.csv')

group_index_ni <- rle(summary_table_no_impute$Pollutant)
group_index_ni <- setNames(group_index_ni$lengths, group_index_ni$values)

tbl_grouped_no_impute <- summary_table_no_impute %>%
  select(-Pollutant) %>%
  kable(row.names = FALSE,
        booktabs = TRUE,
        caption = "Wilcoxon Signed-Rank Tests by Pollutant and Construct (No KNN Imputation)") %>%
  kable_styling(latex_options = "hold_position", font_size = 9, full_width = FALSE) %>%
  pack_rows(index = group_index_ni)

tbl_grouped_no_impute
```

```{r}
get_construct_diff_ni <- function(construct_name) {
  results_no_impute[[which(sapply(results_no_impute, `[[`, "Construct") == construct_name)]]$data %>%
    select(HouseID, score = difference)
}

threat_diff_by_pollutant_ni <- bind_rows(
  get_construct_diff_ni("Perceived Threat (O3)") %>% mutate(pollutant = "O3"),
  get_construct_diff_ni("Perceived Threat (PM2.5)") %>% mutate(pollutant = "PM2.5")
) %>%
  left_join(metadata, by = "HouseID") %>%
  mutate(IO_ratio = if_else(pollutant == "O3", mean_IO_O3_Summer, mean_IO_PM_Summer)) %>%
  select(HouseID, ac.type, pollutant, score, IO_ratio)

threat_diff_by_pollutant_order_ni <- threat_diff_by_pollutant_ni %>%
  filter(!is.na(score)) %>%
  group_by(pollutant) %>%
  mutate(IO_order = dense_rank(IO_ratio)) %>%
  ungroup()

spearman_stats_ni <- threat_diff_by_pollutant_order_ni %>%
  filter(!is.na(IO_ratio)) %>%
  group_split(pollutant) %>%
  map_dfr(function(d) {
    ct <- cor.test(d$score, d$IO_ratio, method = "spearman", exact = FALSE)
    boot_fn <- function(data, indices) {
      cor(data$score[indices], data$IO_ratio[indices], method = "spearman")
    }
    set.seed(3)
    b <- boot::boot(d, boot_fn, R = 2000)
    ci <- boot::boot.ci(b, type = "perc")$percent[4:5]
    tibble(
      pollutant = unique(d$pollutant),
      rho = unname(ct$estimate),
      p_val = ct$p.value,
      ci_lower = ci[1],
      ci_upper = ci[2]
    )
  })

spearman_label_ni <- spearman_stats_ni %>%
  mutate(label = paste0(
    "Spearman's rho = ", round(rho, 2),
    " (95% CI: ", round(ci_lower, 2), ", ", round(ci_upper, 2), "), ",
    "p = ", round(p_val, 3)
  ))

set.seed(3)
IO_vs_diff_threat_order_plt_ni <- ggplot(threat_diff_by_pollutant_order_ni, aes(y = score, x = IO_order)) +
  geom_point(aes(shape = ac.type, color = ac.type)) +
  facet_grid(. ~ pollutant, scales = "free_y") +
  geom_text(data = spearman_label_ni, aes(label = label),
            x = Inf, y = Inf, hjust = 1.05, vjust = 1.5,
            size = 3, fontface = "italic", inherit.aes = FALSE) +
  geom_label_repel(
    data = threat_diff_by_pollutant_order_ni %>%
      filter(HouseID %in% c('H02', 'H05')),
    aes(label = HouseID),
    size = 3,
    nudge_x = -1,
    min.segment.length = .2,
    segment.color = "grey70",
    color = 'grey70',
    box.padding = 0.4,
    show.legend = FALSE,
    alpha = 0.7,
    seed = 5
  ) +
  labs(
    y = "Difference in Threat (post - pre)",
    x = "Rank in Indoor/Outdoor Ratio",
    color = "Home Type",
    shape = "Home Type"
  ) +
  theme_bw() +
  theme(legend.position = "bottom") +
  expand_limits(y = 0.11) +
  scale_x_continuous(limits = c(0, 16), breaks = seq(0, 16, by = 4)) +
  scale_color_manual(values = okabe_ito, name = "House Type") +
  scale_shape_manual(values = c(16, 17), name = "House Type")

IO_vs_diff_threat_order_plt_ni

ggsave(width = 7, height = 4, dpi = 300, units = "in", bg = "white",
       filename = "./Graphics/IO_vs_diff_threat_order_no_impute.tiff")
```